taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-04-02 paper/manuscript.Rmd
updating refs

knitr::opts_chunk$set(cache=FALSE)
```

@@

These issues are best illustrated using a minimal example.  We'll consider the task of combining data on bird extinction risk as assessed by the IUCN [@IUCN] with data on average adult biomass, as estimated in the Elton Traits v1.0 database [@elton-traits.]  To keep the example consise enough for for visual presentation we will focus on a subset involving just 10 species:

>>>>

knitr::opts_chunk$set(cache=FALSE, message=FALSE, warning=FALSE)
```

@@

These issues are best illustrated using a minimal example.  We'll consider the task of combining data on bird extinction risk as assessed by the IUCN [@iucn] with data on average adult biomass, as estimated in the Elton Traits v1.0 database [@elton-traits.]  To keep the example consise enough for for visual presentation we will focus on a subset involving just 10 species:
